Optimal (Multiway) Spatial Joins

### 2024-06-01 5.2.tex
5.2

\noindent \underline{\em Proof of Statement (3).}
 This statement follows from Statement (1). More specifically, we can map each pair $(\bm{t}, r)\in \J(R_1,...,R_{k-3},H',V) \times \contained_{R_{k-2}}(\bm{t})$ to the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r, h, \bm{t}[k-1])$ defined in Statement (1). By Statement (1), this $k$-tuple belongs to $\J_2$. Then, it remains to prove that no two distinct pair $(\bm{t}_1, r_1)$ and $(\bm{t}_2, r_2)$ will be mapped to the same tuple in $\J_2$. Assume to the contrary, $(\bm{t}_1, r_1)$ and $(\bm{t}_2, r_2)$ are mapped to the same tuple $\bm{t} \in \J_2$. Then, $r_1 = \bm{t}[k-2] = r_2$, and $\bm{t}_1[i] = \bm{t}[i] = \bm{t}_2[i]$ for $i \in [k-3]$. Moreover, both $\bm{t}_1[k-2]$ and $\bm{t}_2[k-2]$ are the trimmed segment of $\bm{t}[k-1]$. Since the trimmed segment is unique, $\bm{t}_1[k-2] = \bm{t}_2[k-2]$. Hence, $\bm{t}_1 = \bm{t}_2$, which contradicts the assumption. Therefore, we have $|\J(R_1,...,R_{k-3},H',V)| \le |\J_2| \le \out$, where the second inequality is due to Definition \eqref{eqn:hv:type2:J2}.

>>>>

\noindent \underline{\em Proof of Statement (3).}
We will provide a way to map each pair $(\bm{t'}, r)\in \J(R_1,...,R_{k-3},H',V) \times \contained_{R_{k-2}}(\bm{t})$ to a unique tuple in $\J_2$. Consider an arbitrary pair $(\bm{t'}, r)$. Let $h$ be the full segment of $\bm{t'}[k-2]$. We map $(\bm{t'}, r)$ to the tuple $\bm{t} = (\bm{t}'[1],...,\bm{t}'[k-3], r, h, \bm{t}'[k-1])$. By Statement (1) and the fact that $r\in \contained_{R_{k-2}}(\bm{t'})$, the $k$-tuple $\bm{t}$ belongs to $\J_2$.

It remains to prove that no two distinct pair $(\bm{t}_1, r_1)$ and $(\bm{t}_2, r_2)$ will be mapped to the same tuple in $\J_2$. Assume, on the contrary, $(\bm{t}_1, r_1)$ and $(\bm{t}_2, r_2)$ are mapped to the same tuple $\bm{t} \in \J_2$. Then, $r_1 = \bm{t}[k-2] = r_2$, and $\bm{t}_1[i] = \bm{t}[i] = \bm{t}_2[i]$ for $i \in [k-3]$. Moreover, both $\bm{t}_1[k-2]$ and $\bm{t}_2[k-2]$ are the trimmed segment of $\bm{t}[k-1]$. Since the trimmed segment is unique, $\bm{t}_1[k-2] = \bm{t}_2[k-2]$. Hence, $\bm{t}_1 = \bm{t}_2$, which contradicts the assumption. Therefore, we have $|\J(R_1,...,R_{k-3},H',V)| \le |\J_2| \le \out$, where the second inequality is due to Definition \eqref{eqn:hv:type2:J2}.
